---
title: "lab4_part2"
author: "Kerry Nixon"
date: "10/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Part 2: Two-sample t-test

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))
```


## Exploratory Data Visualization

Exploratory Histogram:
```{r}
ggplot(data = compact_suv, aes( x = cty)) +
  geom_histogram(bins = 15) +
  facet_wrap(~class)
```

### Making a QQ Plot (Quantile-Quantile Plot)

The more linear the relationship, the closer your smaple is to normal distribution. (Unless you specify a different distribution)

```{r}

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~class)

```

### Descriptive Statistics

```{r}

car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(mean_city = mean(cty),
            sd_city = sd(cty),
            n = n())

car_stats

```

### 2-sample t-test


Create vectors containing observations for each sample (city gas mileage)
```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

t.test(x = compact_sample, y = suv_sample)


```










